---
title: "GIt and Github"
subtitle: "FSH 507 Fall 2019"
author: "Your Name"
date: " `r Sys.Date()`"
output:
  ioslides_presentation: default
  powerpoint_presentation: default
  html_document: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(gapminder)
```

# R Markdown

## Getting Started

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown for presentations see <https://bookdown.org/yihui/rmarkdown/presentations.html>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
pressure %>% 
  ggplot(aes(temperature, pressure)) + 
  geom_point()

```




# Materials

# Exercise Ideas

## Clone the repo for this class

* Pull in a change made by Lee Qi

## Create a New Repo

* Create a new repository on GitHub

* Clone it to your computer

* Add to the .gitignore file

* Make a local change, commit it, and push it to GitHub

  - For extra fun, revert back to the repo state before that commit

## Deal with Conflict

- Make a few changes on GitHub

- Change the same things locally

- Try and pull changes from GitHub

- Resolve conflict, and push back to GitHub

## Branching

- Create a branch from your local repo

- Make changes to that branch

- Merge those changes back into the master branch

## Branching and Rebasing 

- Make another branch

- Make and commit changes in that branch

- Go back to master and make changes

- Go back to your branch and [rebase](https://git-scm.com/book/en/v2/Git-Branching-Rebasing) from master

- Merge rebased branch back into master

## Forking and Pull Requests

- Break into teams, and have one person fork the repo their partner made

- Have the fork-er create a branch and make changes to it (ideally with conflicts)

  - Commit and push those changes
  
  - Submit a pull request to the original repo's master branch
  
  - Have owner of repo review and merge pull request


## Resources

[Happy Git and Github for the useR](https://happygitwithr.com/)

[Oh Sh*t, Git!](https://ohshitgit.com/) 
  
  * [Dangit, Git!](https://dangitgit.com/) if you're so inclined

[git documentation itself isn't bad](https://git-scm.com/docs/)

## Fun Resources

[Commits From Last Night](http://www.commitlogsfromlastnight.com/)

[git manual page generator](https://git-man-page-generator.lokaltog.net/)

[starwars intro you commit history!](http://starlogs.net/#DanOvando/Global-Fishery-Potential)








